Centralized Programming for Distributed Control Planes

### 2016-01-27 paper/compilation.tex
minor fix in ABGP policy.

\begin{figure}[t!]
\begin{lstlisting}[frame=single, mathescape=true]
$\Router{A}$
  Match $\PEER=C, \COMM=(3,2)$
    Export $\COMM \leftarrow (4,2), \MED \leftarrow 80, \PEER \leftarrow W$
$\Router{B}$
  Match $\PEER = C, \COMM = (-,2)$
    Export $\COMM \leftarrow (-,3), \COMM \leftarrow \text{noexport},$
           $\MED \leftarrow 81, \PEER \leftarrow W$
  Match $\PEER = C, \COMM = (3,2)$
    Export $\COMM \leftarrow (-,3), \COMM \leftarrow \text{noexport},$
           $\MED \leftarrow 81, \PEER \leftarrow W$
$\Router{C}$-
  Match$[LP=99]$ $\PEER = E, \COMM = (-,2) $
    Export $\COMM \leftarrow (-,2), \PEER \leftarrow B$
  Match $\PEER = D, \COMM = (2,2)$
    Export $\COMM \leftarrow (3,2), \PEER \leftarrow A,B$
$\Router{D}$
  Match $\REGEX{X + Y}$
    Export $\COMM \leftarrow (2,2), \PEER \leftarrow C$
$\Router{E}$
  Match $\REGEX{Z}$
    Export $\COMM \leftarrow (-,2), \PEER \leftarrow C$
\end{lstlisting}
\label{fig:config}
\caption{Abstract BGP router configurations.}
\end{figure}

>>>>

\begin{figure}[t!]
\begin{lstlisting}[frame=single, mathescape=true]
$\Router{A}$
  Match $\PEER=C, \COMM=(3,2)$
    Export $\COMM \leftarrow (4,2), \MED \leftarrow 80, \PEER \leftarrow W$
$\Router{B}$
  Match $\PEER = C, \COMM = (-,2)$
    Export $\COMM \leftarrow (-,3), \COMM \leftarrow \text{noexport},$
           $\MED \leftarrow 81, \PEER \leftarrow W$
  Match $\PEER = C, \COMM = (3,2)$
    Export $\COMM \leftarrow (-,3), \COMM \leftarrow \text{noexport},$
           $\MED \leftarrow 81, \PEER \leftarrow W$
$\Router{C}$
  Match$[LP=99]$ $\PEER = E, \COMM = (-,2) $
    Export $\COMM \leftarrow (-,2), \PEER \leftarrow B$
  Match $\PEER = D, \COMM = (2,2)$
    Export $\COMM \leftarrow (3,2), \PEER \leftarrow A,B$
$\Router{D}$
  Match $\REGEX{X + Y}$
    Export $\COMM \leftarrow (2,2), \PEER \leftarrow C$
$\Router{E}$
  Match $\REGEX{Z}$
    Export $\COMM \leftarrow (-,2), \PEER \leftarrow C$
\end{lstlisting}
\label{fig:config}
\caption{Abstract BGP router configurations.}
\end{figure}
